msc dissertation

### 2021-08-11 msc dissertation code.Rmd
with ordinal

@@

## reproduction of results (interaction between headline veracity and treatment)
### without considering attention check
```{r, message=FALSE}
install.packages("sandwich") 
install.packages("stargazer")
install.packages("lmtest")
library(lmtest)
library(stargazer) 
library(sandwich)

@@

coeftest(lm1, vcovHC)

#z scored
scale(pennystudy2r1$Discern)

@@

#attention1nodi
lm2 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention1nodi)
summary(lm2)

@@

#attention2nodi
lm3 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention2nodi)
summary(lm3)

@@

#attention3nodi
lm4 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention3nodi)
summary(lm4)

@@

@@

anova(glm0,glm1,glm2,glm3,test='LR')

##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
summary(glm4)

@@

glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
glm411 <- glm(measurement ~ condition + condition*headlineveracity, data = attention1, family = binomial(link = "logit"))

@@

#model 1, item_id indicates repeated measurements for each item
mult1 <- lmer (measurement ~ condition + condition*headlineveracity + (1|item_id),
             data = pennys2r1long)
summary(mult1)

@@

ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_discrete(name = "Headline Veracity", labels = c("Fake", "Real"))

@@

### Test (irrelevant)

>>>>

##create a new column that recode item number from fake and real to 1-30, with 1-15 indicate each fake items, 16-30 indicate each real items

pennys2r1longnodi_nona <- within(pennys2r1longnodi_nona,{
  item_id <- NA
  item_id[newstype == "Fake1_1"] <- 1
  item_id[newstype == "Fake1_2"] <- 2
  item_id[newstype == "Fake1_3"] <- 3
  item_id[newstype == "Fake1_4"] <- 4
  item_id[newstype == "Fake1_5"] <- 5
  item_id[newstype == "Fake1_6"] <- 6
  item_id[newstype == "Fake1_7"] <- 7
  item_id[newstype == "Fake1_8"] <- 8
  item_id[newstype == "Fake1_9"] <- 9
  item_id[newstype == "Fake1_10"] <- 10
  item_id[newstype == "Fake1_11"] <- 11
  item_id[newstype == "Fake1_12"] <- 12
  item_id[newstype == "Fake1_13"] <- 13
  item_id[newstype == "Fake1_14"] <- 14
  item_id[newstype == "Fake1_15"] <- 15
  item_id[newstype == "Real1_1"] <- 16
  item_id[newstype == "Real1_2"] <- 17
  item_id[newstype == "Real1_3"] <- 18
  item_id[newstype == "Real1_4"] <- 19
  item_id[newstype == "Real1_5"] <- 20
  item_id[newstype == "Real1_6"] <- 21
  item_id[newstype == "Real1_7"] <- 22
  item_id[newstype == "Real1_8"] <- 23
  item_id[newstype == "Real1_9"] <- 24
  item_id[newstype == "Real1_10"] <- 25
  item_id[newstype == "Real1_11"] <- 26
  item_id[newstype == "Real1_12"] <- 27
  item_id[newstype == "Real1_13"] <- 28
  item_id[newstype == "Real1_14"] <- 29
  item_id[newstype == "Real1_15"] <- 30
})

@@

## reproduction of results (interaction between headline veracity and treatment)
### without considering attention check
```{r, message=FALSE}
library(lmtest)
library(stargazer) 
library(sandwich)

@@

coeftest(lm1, vcov = vcovCL, cluster = ~ ID + item_id)

@@

#Robustness for different levels of attentiveness
##attention above 1
lm2 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention1nodi)
summary(lm2)

@@

coeftest(lm2, vcov = vcovCL, cluster = ~ ID + item_id)

##attention above 2
lm3 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention2nodi)
summary(lm3)

@@

coeftest(lm3, vcov = vcovCL, cluster = ~ ID + item_id)

##attention all 3
lm4 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention3nodi)
summary(lm4)

@@

coeftest(lm4, vcov = vcovCL, cluster = ~ ID + item_id)

@@

glm5 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))

anova(glm0,glm1,glm2,glm3,glm4,test='LR')

##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
summary(glm5)

###odds ratios and 95% CI

@@

## Different attention check group
glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
glm411 <- glm(measurement ~ condition + condition*headlineveracity, data = attention1, family = binomial(link = "logit"))

@@

#Ordinal logistic regression

install.packages("ordinal")
install.packages("ggeffects")

library(ordinal)
library(ggeffects)

ordinaldata <- pennys2r1longnodi_nona

str(ordinaldata)
ordinaldata$measurement <- as.factor(ordinaldata$measurement)

ordinal <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata, link = "logit")

summary(ordinal)

exp(coef(ordinal))

ggpredict_ordinal <- ggpredict(ordinal, terms = c("condition","headlineveracity"))
ggpredict_ordinaldata = data.frame(ggpredict_ordinal)

ggpredict_ordinal
str(ggpredict_ordinaldata)

ggpredict_ordinaldata$x = factor(ggpredict_ordinaldata$x)
levels(ggpredict_ordinaldata$x) = c("False", "True")
colnames(ggpredict_ordinaldata)[c(1, 5,6)] =c("Headlineveracity", "Rating", "group")
levels(ggpredict_ordinaldata$group) = c("Control", "Treatment")
ggpredict_ordinaldata

ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + theme_minimal() +facet_wrap(~group)

@@

ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True"))

@@

### Tests (irrelevant)

#z scored
scale(pennystudy2r1$D)

#model 1, item_id indicates repeated measurements for each item
mult1 <- lmer (measurement ~ condition + condition*headlineveracity + (1|item_id),
             data = pennys2r1longnodi_nona)
summary(mult1)
